---
title: 'Developing Data Projects: Course Project'
author: "Miguel Adarlo"
date: "2023-08-09"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Introduction

The iris dataset has the measurements of 50 flowers from 3 species: *Iris setosa*, *versicolor*, and *virginica*. These measurements are in centimeters, and measure the following variables: sepal length and width, and petal length and width.

The goal of this project is to build a Shiny App that can plot these variables, as well as provide a regression line per species.

## Example Graph
```{r libraries to load}
library(ggplot2)
library(plotly)
data(iris)
```

``` {r sample plot}
irisPlot <- ggplot(data = iris, aes(x = Petal.Length, y = Sepal.Length, color = Species)) +
        geom_point() +
        geom_smooth(method = lm, formula=y~x)

ggplotly(irisPlot)
```
You can hover over the graph to see specific points.

## How to use

The side panel has two sets of radio buttons. The first set picks the variable to be plotted on the x-axis. The second set picks the variable to be plotted on the y-axis.

The checkbox selects if the regression lines will be shown or not. 

In order to update the plot, you must press the Create Plot button first.

## Links related to the project

Shiny App:
<https://irj3fx-miguel0antonio-adarlo.shinyapps.io/Developing_Data_Products-Course_Project/>

GitHub for Project:
<https://github.com/Miguel-Adarlo/Course-Project-Developing-Data-Products-Week-4>




